Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-03 aggexplain/abstract.tex
fix figures and some citations
much more text

@@

\begin{contributions}{Foo}
\item \todo{TODO}
\end{contributions}

>>>>

\begin{contributions}{What is the impact of aggregating instance-level explanations?}
\item Histograms can effectively be used to aggregate instance-level explanations and compare subsets.
\item Aggregating instance-level explanations significantly outperform inspecting individual explanations or aggregating without explanations in detecting biases in the input data.
\item Inspecting individual instance-level explanations can be misleading and hurt detecting biases in the input data.
\item Aggregated instance-level explanations allow to detect biases equally well as in a table without explanations while being more scalable.
\end{contributions}

@@

### 2018-04-03 aggexplain/experiment.tex
much more text

\subsubsection{Aggregated Condition}
The user interface for the aggregated condition represents the distribution of feature values as histograms.
Feature names are shown above the histogram and the histograms are arranged left to right row-wise and top to bottom.
For the condition with explanations available, a small bar chart next to the feature name indicates the average weight of this feature.
In this condition, the histograms are ordered by descending magnitude of average feature weights.
The averages are computed for each subset separately.
The order is, more specifically, based on the average of the subsets' average weights, which allows features to appear first that are only important under certain conditions.
If no explanations are provided, the order is alphabetically.

>>>>

\subsubsection{Aggregated Condition}
The user interface for the aggregated condition represents the distribution of feature values as histograms, similar to \cite{seekaview}.
Feature names are shown above the histogram and the histograms are arranged left to right row-wise and top to bottom.
For the condition with explanations available, a small bar chart next to the feature name indicates the average weight of this feature.
In this condition, the histograms are ordered by descending magnitude of average feature weights.
The averages are computed for each subset separately.
The order is, more specifically, based on the average of the subsets' average weights, which allows features to appear first that are only important under certain conditions.
If no explanations are provided, the order is alphabetically.

### 2018-04-03 aggexplain/results.tex
much more text

However, we see a strong decline in correctness when adding explanations to tables (p-value Fisher's $0.0311$, $\chi^2$ $0.0320$).
At first, we were puzzled at this counter-intuitive result and we double and triple checked that those results were not a simple mix-up in conditions.
We hypothesize that, having explanations at hand in a table, focuses the attention of participants to fewer instances and additionally makes them more confident that they fully understood the model.
This extrapolation from few instances aligns with the findings of Stumpf~\etal~\cite{harmful}, who found that explanations can be harmful in certain circumstances.

@@

$25\%$ of people who correctly identified the bias still opted to trust the biased model more, due to the higher reported accuracy of the model.
A further $8\%$ who identified the bias trusted both models equally.
Again, this aligns with the findings of Stumpf~\etal~\cite{harmful} that trust in the machine learning model may \emph{override} people's initial intuition about its performance.

>>>>

However, we see a strong decline in correctness when adding explanations to tables (p-value Fisher's $0.0311$, $\chi^2$ $0.0320$).
At first, we were puzzled at this counter-intuitive result and we double and triple checked that those results were not a simple mix-up in conditions.
We hypothesize that, having explanations at hand in a table, focuses the attention of participants to fewer instances and additionally makes them more confident that they fully understood the model.
This extrapolation from few instances aligns with the findings of Stumpf~\etal~\cite{harmful}, who found that explanations can be harmful in certain circumstances, and shows that the findings also apply to a tabular representation of the explanations.

@@

$25\%$ of people who correctly identified the bias still opted to trust the biased model more, due to the higher reported accuracy of the model.
A further $8\%$ who identified the bias trusted both models equally.
Again, this aligns with the findings of Stumpf~\etal~\cite{harmful} that trust in the machine learning model may \emph{override} people's initial intuition about its performance, and shows that the findings also apply to a tabular representation of the explanations.

### 2018-04-03 explainer/abstract.tex
much more text

>>>>

\begin{contributions}{How can black-box explanations help diagnose model errors?}
\item The model diagnostic workflow enables a scalable understanding of local decision making of a predictive model.
\item Aggregation of instance-level explanations allows for semantic validation of the input data.
\item A model can only perform as well as its input data.
\item Gaining insights about the limitations of a model in turn helps with feature engineering on the input data.
\end{contributions}

### 2018-04-03 infuse/use_case.tex
much more text

\begin{figure*}[ht]
\centering
\resizebox{0.9\linewidth}{!}{%
\begin{tikzpicture}
\newcommand*{\imgwidth}{3.7cm}
\newcommand*{\boxsize}{0.437cm}
\newcommand*{\boxpos}{(.295, -.18)}
\newcommand*{\rightimagepos}{(4.8, 0)}
\newcommand*{\leftimagepos}{(0, 0)}
\node[inner sep=0pt] at \leftimagepos
    {\includegraphics[width=\imgwidth]{infuse/ap}};
\node[inner sep=0pt] at \leftimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/ap}}};
\node[inner sep=2.5pt,very thick, text height=\boxsize] (zoom)
at \boxpos
    {\hspace*{\boxsize}};
\node[inner sep=-0.05pt] (lasso) at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\draw (zoom.north west) -- (lasso.north west);
\draw (zoom.south west) -- (lasso.south west);
\draw (zoom.north east) -- (lasso.north east);
\draw (zoom.south east) -- (lasso.south east);
\node[very thick, draw=red!90, text height=\boxsize]
at \boxpos {\hspace*{\boxsize}};
\node[inner sep=0pt, very thick] at \rightimagepos
    {\includegraphics[width=\imgwidth]{infuse/lasso}};
\node[inner sep=0pt, very thick, draw=red!90] at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\end{tikzpicture}%
}
\caption[The scatter-plot view allows users to compare multiple types of rankings.]{
The scatter-plot view allows users to compare multiple types of rankings.  In the case study, users became curious of the medication features that were chosen by only half of the models.  When reviewing these medications with domain experts, it became clear that features picked by the upper-half algorithms were as clinically significant as those picked by the bottom-half.  This indicates that merging results from feature selection algorithms makes sense for this predictive model.
}
\label{fig:usecase2}
\end{figure*}

>>>>

\begin{figure*}[ht]
\centering
\resizebox{0.9\linewidth}{!}{%
\begin{tikzpicture}
\newcommand*{\imgwidth}{3.7cm}
\newcommand*{\boxsize}{0.437cm}
\newcommand*{\boxpos}{(.295, -.18)}
\newcommand*{\rightimagepos}{(4.8, 0)}
\newcommand*{\leftimagepos}{(0, 0)}
\node[inner sep=0pt] at \leftimagepos
    {\includegraphics[width=\imgwidth]{infuse/ap}};
\node[inner sep=0pt] at \leftimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/ap}}};
\node[inner sep=2.5pt,very thick, text height=\boxsize] (zoom)
at \boxpos
    {\hspace*{\boxsize}};
\node[inner sep=-0.05pt] (lasso) at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\draw (zoom.north west) -- (lasso.north west);
\draw (zoom.south west) -- (lasso.south west);
\draw (zoom.north east) -- (lasso.north east);
\draw (zoom.south east) -- (lasso.south east);
\node[very thick, draw=red!90, text height=\boxsize]
at \boxpos {\hspace*{\boxsize}};
\node[inner sep=0pt, very thick] at \rightimagepos
    {\includegraphics[width=\imgwidth]{infuse/lasso}};
\node[inner sep=0pt, very thick, draw=red!90] at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\end{tikzpicture}%
}
\caption[The scatter-plot view allows to compare multiple types of rankings.]{
The scatter-plot view allows users to compare multiple types of rankings.  In the case study, users became curious of the medication features that were chosen by only half of the models.  When reviewing these medications with domain experts, it became clear that features picked by the upper-half algorithms were as clinically significant as those picked by the bottom-half.  This indicates that merging results from feature selection algorithms makes sense for this predictive model.
}
\label{fig:usecase2}
\end{figure*}

### 2018-04-03 tex/aggexplain.tex
much more text

\section{General Discussion}
\todo{TODO}

>>>>

\section{General Discussion}
In our study we found that aggregating instance-level explanations using histograms and subset comparison provides a scalable alternative to inspecting tabular data manually for finding biases in the input data of a predictive model.
We only tested finding biases that were possible to find in all of our four conditions.
It would be easy to construct a bias that is impossible to find looking at a table of the data, but this would be an unfair comparison.
Thus, our method is more scalable, since it enables to find a super-set of biases detectable in tables.

However, our method requires both aggregation and instance-level explanations.
Without either of those, performance in finding biases decreased significantly.
This also brings light to the issue that individual instance-level explanations can be misleading and thus harmful.
We could confirm, that the findings of Stumpf~\etal~\cite{harmful}, which show that inspecting individual instance-level explanations can lead to harmful extrapolations of the model's behavior, also apply to a tabular representation.
However, our method overcomes this harmfulness.

Furthermore, even when confronted with evidence of an erroneous data set a quarter of the participants still preferred the model with higher accuracy but incorrect data.
This implies a strong trust in statistical accuracy whose perception needs to be reevaluated.

The presented work shows the effectiveness of aggregated instance-level explanations, and in extension of the previously presented Model Diagnostic workflow, but it also opens up further research opportunities.

### 2018-04-03 tex/introduction/contribution.tex
decision tree
much more text

\subsection{\infuse}
In the first stage we analyze and compare different feature selection strategies. Feature selection is a pre-processing step that, unlike feature engineering, algorithmically determines the possible predictive impact of a feature. Only the most impactful features are then used as input for the predictive modeling process. This is often necessary as a larger number of features require significantly more training examples to accurately represent the valid input space without losing predictive qualities. As feature selection algorithms use similar statistical tools as many predictive modeling techniques it seems plausible to infer the importance of features in the context of decision making through feature selection in a model agnostic way.

@@

\subsection{\prospector}
In the second stage we explore the influence of features in the decision making process of predictive models through a technique called partial dependence. Partial dependence computes feature impact on model outcomes by systematically probing the model with artificial inputs. That is, while keeping the rest of the input values the same, the inspected feature assumes all possible values showing the relationship of feature values to the prediction score. Aggregated over all observed instances, the general behavior of the model with respect to a given feature can be inferred. By computing a novel feature importance score from partial dependence relationships unusual and interesting relations can be found quickly without having to inspect all, often several thousand, features.

@@

We use this workflow to analyze a predictive modeling problem revolving patient admission to a hospital, of patients in the emergency department of said hospital. Accurately predicting whether a patient eventually gets admitted to the hospital helps reducing costs. The major limiting factor of this prediction task is the need for input features readily, and electronically, available at the earliest point possible. To this extend we initially used features of prescribed medications as this information is immediately available electronically. Our analysis showed that there are clear groups of patients where the predictive model is very helpful. However, there are some groups of patients where it is impossible for the predictive model to make accurate predictions given the provided information. One of those groups is patients receiving Diatrizoate Meglumine, a contrast medium for CAT or PET scans. This medication only indicates that a scan was performed, but does not carry information about the result of the scan. However, the result of the scan is the deciding factor whether a patient needs further care or can get sent home. Thus, with the given information it is impossible for the predictive model to make a decision that performs better than random guessing. Including more information in the form of additional features does indeed help with this problem but pushes the time when a decision can be made further back. One possible solution is to utilize the predictive model only for the confident groups of patients and wait for the doctors' decisions in other cases. This example illustrates that it is not only possible to \textbf{understand decision making} of a predictive model through the \textbf{model diagnostic workflow} based on \textbf{aggregated instance level explanations}, but also how it can be applied for \textbf{semantic validation} and \textbf{feature engineering} on the input data.

\begin{table}[t]
     \begin{tabular}{l|c|c|c} 
     \textbf{Approach} & \makebox[0pt][l]{\textbf{Instances}}\phantom{Aggregated} & \textbf{Aggregated} & \makebox[0pt][l]{\textbf{Global}}\phantom{Aggregated} \\ 
     \hline
     \hline
     \infuse & & & X \Tstrut\\
     \hline
     \prospector & X & & X \Tstrut\\
     \hline
     \textit{Model diagnostic workflow} & & X & \Tstrut\\
    \end{tabular}
    \centering
    \vspace*{-0.5em}
    \caption[Locality of decision analyses of the presented approaches.]{Locality of decision analyses of the presented approaches. \textbf{Instances} refers to analyzing decisions for one instance at a time. \textbf{Aggregated} refers to analyzing decisions for groups of instances and \textbf{Global} refers to analyzing decisions globally without inspecting decisions for individual instances.}
    \vspace*{-0.75em}
    \label{tab:locality}
\end{table}

\subsection{TODO}
\todo{fill in latest work}
In addition to those promising results, there is still work to do.
It still needs to be shown that the proposed workflow of statistical analysis of instance-level explanations can be successfully applied to other data types than binary feature vectors, such as numerical features or highly redundant features such as found in images.
Early results in this direction indicate that it might be beneficial to abandon the focus on features to explain machine learning models, but rather focus on instances directly.
That is using instance-level explanations to obtain groups of \emph{instances} with similar behavior and then visualize those groups (\eg, using techniques proposed by \cite{seekaview}) in order to \emph{implicitly} explain them.
This provides more flexible explanations than those proposed earlier as their capability goes beyond ``Feature A and feature B positively impact the prediction for this group of instances" to also allow insights of the form ``The number of circles formed by black pixels contribute positively to the prediction" which would be very difficult to formulate by a machine but are easily formulated by humans using visualizations.
Furthermore, we are going to run a study on the implications on confidence in and trust of machine learning models when using different explanation approaches.
\todo{END?}

>>>>

\subsection{\emph{\infuse}}
In the first stage we analyze and compare different feature selection strategies. Feature selection is a pre-processing step that, unlike feature engineering, algorithmically determines the possible predictive impact of a feature. Only the most impactful features are then used as input for the predictive modeling process. This is often necessary as a larger number of features require significantly more training examples to accurately represent the valid input space without losing predictive qualities. As feature selection algorithms use similar statistical tools as many predictive modeling techniques it seems plausible to infer the importance of features in the context of decision making through feature selection in a model agnostic way.

@@

\subsection{\emph{\prospector}}
In the second stage we explore the influence of features in the decision making process of predictive models through a technique called partial dependence. Partial dependence computes feature impact on model outcomes by systematically probing the model with artificial inputs. That is, while keeping the rest of the input values the same, the inspected feature assumes all possible values showing the relationship of feature values to the prediction score. Aggregated over all observed instances, the general behavior of the model with respect to a given feature can be inferred. By computing a novel feature importance score from partial dependence relationships unusual and interesting relations can be found quickly without having to inspect all, often several thousand, features.

@@

We use this workflow to analyze a predictive modeling problem revolving patient admission to a hospital, of patients in the emergency department of said hospital. Accurately predicting whether a patient eventually gets admitted to the hospital helps reducing costs. The major limiting factor of this prediction task is the need for input features readily, and electronically, available at the earliest point possible. To this extend we initially used features of prescribed medications as this information is immediately available electronically. Our analysis showed that there are clear groups of patients where the predictive model is very helpful. However, there are some groups of patients where it is impossible for the predictive model to make accurate predictions given the provided information. One of those groups is patients receiving Diatrizoate Meglumine, a contrast medium for CAT or PET scans. This medication only indicates that a scan was performed, but does not carry information about the result of the scan. However, the result of the scan is the deciding factor whether a patient needs further care or can get sent home. Thus, with the given information it is impossible for the predictive model to make a decision that performs better than random guessing. Including more information in the form of additional features does indeed help with this problem but pushes the time when a decision can be made further back. One possible solution is to utilize the predictive model only for the confident groups of patients and wait for the doctors' decisions in other cases. This example illustrates that it is not only possible to \textbf{understand decision making} of a predictive model through the \textbf{model diagnostic workflow} based on \textbf{aggregated instance-level explanations}, but also how it can be applied for \textbf{semantic validation} and \textbf{feature engineering} on the input data.

\begin{table}[t]
     \begin{tabular}{l|c|c|c} 
     \textbf{Approach} & \makebox[0pt][l]{\textbf{Instances}}\phantom{Aggregated} & \textbf{Aggregated} & \makebox[0pt][l]{\textbf{Global}}\phantom{Aggregated} \\ 
     \hline
     \hline
     \infuse & & & X \Tstrut\\
     \hline
     \prospector & X & & X \Tstrut\\
     \hline
     \textit{Model diagnostic workflow} & & X & \Tstrut\\
    \end{tabular}
    \centering
    \caption[Locality of decision analyses of the presented approaches.]{Locality of decision analyses of the presented approaches. \textbf{Instances} refers to analyzing decisions for one instance at a time. \textbf{Aggregated} refers to analyzing decisions for groups of instances and \textbf{Global} refers to analyzing decisions globally without inspecting decisions for individual instances.}
    \label{tab:locality}
\end{table}

\subsection{User Study on Aggregating Explanations}
In order to show the generalizability of the Model Diagnostic Workflow we conducted a user study to explore the effectiveness of aggregated instance-level explanations in detecting biases in the input data.

First, we generalized aggregating instance-level explanations to numerical input data.
We achieved this by using histograms of the input features, similar to \cite{seekaview}, ordered by the features' aggregated importance.
Furthermore, we allowed the comparison of selected, meaningful, subsets to each other.
Then, we compared this aggregated representation to the commonly used approach of individually inspecting instance-level explanations one-by-one using a tabular representation.

\todo{fill in latest work}
% In addition to those promising results, there is still work to do.
% It still needs to be shown that the proposed workflow of statistical analysis of instance-level explanations can be successfully applied to other data types than binary feature vectors, such as numerical features or highly redundant features such as found in images.
% Early results in this direction indicate that it might be beneficial to abandon the focus on features to explain machine learning models, but rather focus on instances directly.
% That is using instance-level explanations to obtain groups of \emph{instances} with similar behavior and then visualize those groups (\eg, using techniques proposed by \cite{seekaview}) in order to \emph{implicitly} explain them.
% This provides more flexible explanations than those proposed earlier as their capability goes beyond ``Feature A and feature B positively impact the prediction for this group of instances" to also allow insights of the form ``The number of circles formed by black pixels contribute positively to the prediction" which would be very difficult to formulate by a machine but are easily formulated by humans using visualizations.
% Furthermore, we are going to run a study on the implications on confidence in and trust of machine learning models when using different explanation approaches.
% \todo{END?}

### 2018-04-03 tex/introduction/motivation.tex
much more text

@@

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/emradio.png}
\caption[Programmable circuit to automatically design oscillators.]{
The physical programmable circuit used by Bird and Layzell \cite{Bird:2002:ERI:1251972.1252349} for solving the task of automatically designing oscillators.
}
\label{figs:emradio}
\end{figure}
% https://people.duke.edu/~ng46/topics/evolved-radio.pdf

\par \noindent (3)
\todo{toaster example}
% \cite{2017arXiv171209665B}
% https://arxiv.org/pdf/1712.09665.pdf
% https://arxiv.org/abs/1712.09665

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/adversarialtoaster.png}
\caption[The adversarial patch.]{
The adversarial patch. When put on any image, the image will get classified as toaster.
}
\label{figs:toaster}
\end{figure}

@@

@@

% There has been research...specialized models
% In order for a technique to be effectively useful for a human it needs to have few restrictions \todo{}
* black-box vs. white-box
* reasons for black box
\todo{problem statement}

The above example illustrates the need for human understanding and supervision in machine learning and the incorrect correct result could easily be identified since the authors used a special, intelligible, model. However, not all models used in machine learning are, or even attempt to be, easily interpretable by human experts. To counteract this, visual analytics has been successfully used to visualize machine learning processes in order to understand and gain insights into predictive models. Visual analytics is the area of studying interactive graphical representations of abstract information with the help of computational and statistical procedures, in order to effectively analyze complex data. With regards to understanding the decision making of predictive machine learning models, there are two main strategies: white-box and black-box analysis \cite{class_signatures}.

@@

\newcommand\Tstrut{\rule{0pt}{2.5ex}}
\begin{table}
     \begin{tabular}{cl|cl} 
     & \textbf{White-box} & & \textbf{Black-box} \\
     \hline
     \hline
    $\oplus$ & Deep understanding of decisions & $\ominus$ & External behavior only \Tstrut \\
    $\oplus$ & Always reflects the true & $\ominus$ & Not guaranteed to reflect model \Tstrut \\
    & decision making process & & decisions truthfully in all cases \\
    $\oplus$ & Full internal state available & $\ominus$ & Limited knowledge of \Tstrut \\
    & & & model specifics \\
    \hline
    $\ominus$ & Model specific techniques & $\oplus$ & Reusable techniques \Tstrut \\
    $\ominus$ & Complexity / interpretability & $\oplus$ & Complexity / interpretability \Tstrut \\ 
    & data and model dependent & & independent of data and model \\
    $\ominus$ & Switching to interpretable model & $\oplus$ & No performance considerations \Tstrut \\
    & incurs performance penalty & & necessary \\
    \end{tabular}
    \centering
    \vspace*{-0.5em}
    \caption[Comparison of black-box and white-box explanation strategies.]{Comparison of black-box and white-box explanation strategies. $\oplus$ indicates advantages of a technique while $\ominus$ indicates drawbacks.}
    \vspace*{-0.75em}
    \label{tab:blackvswhite}
\end{table}

>>>>

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/emradio.png}
\caption[Programmable circuit to automatically design oscillators.]{
The physical programmable circuit used by Bird and Layzell \cite{Bird:2002:ERI:1251972.1252349} for solving the task of automatically designing oscillators.
}
\label{figs:emradio}
\end{figure}

@@

% https://people.duke.edu/~ng46/topics/evolved-radio.pdf

\par \noindent (3)
Brown~\etal~\cite{2017arXiv171209665B} exploited weaknesses of popular image classification machine learning models in order to create an adversarial patch.
This adversarial patch, when added to any image will overwrite the original classification of the model and force it to predict the desired outcome.
Concretely, the patch seen in Figure~\ref{figs:toaster} forces image classification models to predict any image as toaster.
The existence of such patches illustrates the fragility of modern machine learning models to unexpected input data, which leads to surprising and counter-intuitive mispredictions.
% \cite{2017arXiv171209665B}
% https://arxiv.org/pdf/1712.09665.pdf
% https://arxiv.org/abs/1712.09665

@@

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/adversarialtoaster.png}
\caption[The adversarial patch.]{
The adversarial patch. When put on any image, the image will get classified as toaster~\cite{2017arXiv171209665B}.
}
\label{figs:toaster}
\end{figure}

@@

The above examples illustrate the need for human understanding and supervision in machine learning.
However, those cases required intricate understanding of the used machine learning models and are not easily generalized to other techniques.
For example, in the case of Caruana~\etal\cite{Caruana:2015:IMH:2783258.2788613}, the incorrect correct result was easily identified since the authors used a special, intelligible, model.
However, not all models used in machine learning are, or even attempt to be, easily interpretable by human experts.
To counteract this, visual analytics has been successfully used to visualize machine learning processes in order to understand and gain insights into predictive models \todo{cite vis papers last year}. Visual analytics is the area of studying interactive graphical representations of abstract information with the help of computational and statistical procedures, in order to effectively analyze complex data. With regards to understanding the decision making of predictive machine learning models, there are two main strategies: white-box and black-box analysis \cite{class_signatures}.

@@

\newcommand\Tstrut{\rule{0pt}{2.5ex}}
\begin{table}
     \begin{tabular}{cl|cl} 
     & \textbf{White-box} & & \textbf{Black-box} \\
     \hline
     \hline
    $\oplus$ & Deep understanding of decisions & $\ominus$ & External behavior only \Tstrut \\
    $\oplus$ & Always reflects the true & $\ominus$ & Not guaranteed to reflect model \Tstrut \\
    & decision making process & & decisions truthfully in all cases \\
    $\oplus$ & Full internal state available & $\ominus$ & Limited knowledge of \Tstrut \\
    & & & model specifics \\
    \hline
    $\ominus$ & Model specific techniques & $\oplus$ & Reusable techniques \Tstrut \\
    $\ominus$ & Complexity / interpretability & $\oplus$ & Complexity / interpretability \Tstrut \\ 
    & data and model dependent & & independent of data and model \\
    $\ominus$ & Switching to interpretable model & $\oplus$ & No performance considerations \Tstrut \\
    & incurs performance penalty & & necessary \\
    \end{tabular}
    \centering
    \caption[Comparison of black-box and white-box explanation strategies.]{Comparison of black-box and white-box explanation strategies. $\oplus$ indicates advantages of a technique while $\ominus$ indicates drawbacks.}
    \label{tab:blackvswhite}
\end{table}
